%% start of file `template.tex'.
%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'
\moderncvcolor{blue}                               % color options 'black', 'blue' (default), 'burgundy', 'green', 'grey', 'orange', 'purple' and 'red'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
\setlength{\footskip}{40.8pt}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Ivan}{Ogloblin}                             % optional, remove / comment the line if not wanted
\firstname{Ivan} % Your first name
\lastname{Ogloblin} % Your last name
% optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file                               % optional, remove / comment the line if not wanted

% bibliography adjustements (only useful if you make citations in your resume, or print a list of publications using BibTeX)
%   to show numerical labels in the bibliography (default is to show no labels)
\makeatletter\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}\makeatother
%   to redefine the bibliography heading string ("Publications")
%\renewcommand{\refname}{Articles}

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
	%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
	\clearpage
	%-----       letter       ---------------------------------------------------------
	% recipient data
	%	\recipient{Support Programm at IMPA}{Company, Inc.\\123 somestreet\\some city}
	\recipient{Cover Letter}{}
%	\date{June 18, 2022}
	\opening{Dear Sir or Madam,}
	\closing{Yours truly,}
	%	\enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
	\makelettertitle
	
	I am applying for the Senior Developer position on the Rider GameDev Tools team. This role strongly aligns with my background and long-term interests: game development, developer tooling, and technically demanding systems that serve other engineers.

	I started programming through game development. During high school, I spent several years working intensively with Unity, building PC and mobile games and experimenting with procedural generation and gameplay systems. That period gave me a practical understanding of game engines from a developer’s perspective and sparked a lasting interest in how tools and engines support iteration, debugging, and content creation.
	
	My academic and professional path later led me into quantum computing research and engineering. In this area, I focused on algorithm design, performance optimization, and building reliable infrastructure for simulations and research workflows. I mostly worked in C++, implemented performance-critical components, and achieved substantial speedups by rethinking data structures, execution models, and native bindings. All of this work required deep understanding of complex systems, careful debugging, and writing code intended to be used and extended by others.
	
	Alongside research work, I consistently took responsibility for improving developer-facing infrastructure. At QC Design, I redesigned how tests, public notebooks, and documentation were structured and maintained, unifying previously separate systems into a single source of truth. This significantly reduced friction when making changes and improved maintainability for the entire team. I have also worked on internal AI tooling, including designing and refining prompts intended for daily use by developers.
	
	Today, my interest in game development has rekindled with a clearer focus on tooling rather than content alone. I am particularly interested in areas such as shader language support, live coding, performance profiling for large projects, and AI-assisted features that meaningfully improve developers’ day-to-day work. I am eager to deepen my understanding of modern game development tooling and to contribute to features that operate at the boundary between IDEs and game engines.
	
	I am super siked for the opportunity to bring my background in game development, high-performance systems, and developer tooling to the Rider team. I am sure I will be a great fit and I can't wait to discuss my qualifications in more detail at an interview.
	
	%	\makeletterclosing
	% \vspace*{\fill}
	\title{}
	\phone[mobile]{+49~15162630532}
	\address{Erhard-Grözinger-Straße, 75}{Blaustein}{Germany}
	\email{ivanogloblin2022@gmail.com}
	\social[github]{ivanoglo}   
	%	\makecvtitle
	\makeletterclosing
	\name{}{}
	%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}


%% end of file `template.tex'.
