\documentclass[a4paper,11pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=blue}

% Sender info
\signature{Ivan Ogloblin}
\address{Bismarckring 64\\89077 Ulm, Germany\\+49 0151 6263 0532\\ivanogloblin2022@gmail.com}
\date{\today}

\begin{document}

% Recipient and subject
\begin{letter}{Next Kraftwerke GmbH\\Software \& Data Services Unit\\Cologne-Ehrenfeld}
\opening{Dear Hiring Team,}

I'm excited to apply for the Python Software Developer -- Forecasting role. Your work on data pipelines and forecasts is exactly the kind of chalange I want to take on.

\textbf{I would be a good fit for your team, because my skillset matches your needs and my interests align with your company's mission.} During my master's I studied quantum physics processes and spent the last years building real software around hardware error models. In production, I developed a fast-performing Python library with \texttt{C++}, worked with customers, and delivered features under tight constraints. Before that I worked as a backend developer and I learned to design clear ETL and ML pipelines that give accurate, reliable results. I care about low-latency code and analysing big data.

I've learned a lot in quantum computing and feel I've reached a local peak there for now. The field moves, but I want more hands-on, ambitious work with real users and real impact. Energy forecasting fits me: hard problems, real operations, and a team that values ownership and collaboration. I am sure that my skills are excelent for the job and that I can be a great fit for your team.

I'm ready to relocate to Cologne or work hybrid/remote. I'd be happy to walk you through my expertise and show you how I can help. Thank you for your time!

\closing{Best regards,}

\end{letter}

\end{document}
