%% start of file `template.tex'.
%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[12pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'
\moderncvcolor{blue}                               % color options 'black', 'blue' (default), 'burgundy', 'green', 'grey', 'orange', 'purple' and 'red'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Ivan}{Ogloblin}                             % optional, remove / comment the line if not wanted
\firstname{Ivan} % Your first name
\lastname{Ogloblin} % Your last name arguments can be omitted or provided empty
\email{ivanogloblin2022@gmail.com}                               % optional, remove / comment the line if not wanted                         % optional, remove / comment the line if                            % optional, remove / comment the line if not wanted
\social[github]{ivanoglo}                              % optional, remove / comment the line if not wanted
% optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file                               % optional, remove / comment the line if not wanted

% bibliography adjustements (only useful if you make citations in your resume, or print a list of publications using BibTeX)
%   to show numerical labels in the bibliography (default is to show no labels)
\makeatletter\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}\makeatother
%   to redefine the bibliography heading string ("Publications")
%\renewcommand{\refname}{Articles}

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
	%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
	\clearpage
	%-----       letter       ---------------------------------------------------------
	% recipient data
	%	\recipient{Support Programm at IMPA}{Company, Inc.\\123 somestreet\\some city}
	\recipient{Cover letter}{}
	\date{\today}
	\opening{Dear Multiverse Computing Hiring Team,}
	\closing{Yours faithfully,}
	%	\enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
	\makelettertitle

I am writing to apply for the Quantum Engineer Intern position. I am already a quantum software engineer with over a year of hands-on experience, and I want to work at Multiverse Computing specifically because I want to evolve into a consultant — someone who bridges the gap between quantum technology and real industry needs. My ambition is to develop the business side of quantum computing, working directly with companies in finance, energy, manufacturing, and cybersecurity to understand their biggest challenges and map them to practical solutions.

In my current role, I lead a small team (up to four people) and introduced a pipeline that boosted simulation speeds by over 10,000 times for complex noise models. I always knew that raw performance is crucial when offering the best solutions to the customer, and this work further strengthened my understanding of customer needs. I also contributed to real-world applications by mapping route-planning task to QUBO form for an oil company, which showed me how even the most intricate operational problems boil down to solvable math and optimization.

Working closely with diverse partners excites me because I see how different industries can transform massive, seemingly impossible tasks through faster and more intelligent computation. Being a consultant means I get to engage with leaders in each field, hear their unique challenges, and help craft solutions that draw upon quantum technology's strengths. I'm eager to provide that link between quantum computing and the concrete business results, and I believe Multiverse's focus on real, industry-driven software solutions is the perfect place to do this.

I'm certain I have the technical depth to succeed in this position as my background in fast simulations, noise modeling, algorithm development and quantum theory aligns well with Multiverse's standards. Now, I want to deepen my client-facing skills, learn from top experts, and shape quantum projects that truly solve core problems. Being at an early stage in my career, I view Multiverse as an excellent environment to grow from a capable engineer into a seasoned consultant.

Thank you for your consideration. I'll be waiting for the opportunity to discuss how my expertise and ambitions can support Multiverse Computing's ongoing success.
	
	%	\makeletterclosing
	\title{}
	\phone[mobile]{+49~015162630532}
	\address{Bismarckring, 64}{Ulm}{Germany}
	\email{ivanogloblin2022@gmail.com}
	%	\makecvtitle
	\makeletterclosing
	\name{}{}
	%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}


%% end of file `template.tex'.
